Viscous Erosion in Porous Media

### 2018-01-30 docs/methods/erosion_methods.tex
Methods paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{s:results}
With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow. We first discuss the case of a single eroding body, as certain features can be predicted analytically and thus used for validation. We then discuss the erosion of multiple bodies and highlight important differences compared to the single-body case.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{s:results}
With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow. We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation. We then discuss the erosion of multiple bodies and highlight important differences that arise as compared to the single-body case.
